Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
related work section update

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1982 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems'' later evolved in a more broader sense of  Computer-supported collaboration (CSC). The Social computing is another shift, which is a generic term refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in computing rather than broader sense of

>>>>

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1982 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems''. This concept later evolved into a more broader sense of  Computer-supported collaboration (CSC). The Social computing is another shift, which is a generic term refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in `computing' rather than `collaboration'. Similarly, the Human Computation is another paradigm towards this computational direction, which utilize human processing power to solve problems that computers cannot yet solve. All these three mentioned fields has overlapping in the their concepts and they are mainly popularised in the computer science. In the Web 2.0 era, there are few new broader concepts/buzzword emerged on the idea of utilising the human power which are not only used in computer science, but also in other fields such as social science, business etc. For example, crowding sourcing is an idea that taking a job traditionally performed by a designated agent and outsourcing it to an undefined, generally large group of people in the form of an open call. As it is argued in Surowieckis the wisdom of crowds that the aggregation of information in groups, resulting in decisions that are often better than could have been made by any single member of group. Open Innovation advocate the similar idea with empathising on the innovation in firms.

Open Innovation is another example,
